Quality Metrics for SKOS Vocabularies

### 2012-03-12 analysis.tex
added acknowledgements draft and updated analyzed vocab table

\subsection{Vocabulary Data Set}

\todo{CM}{Add dataset table so that we know how much space this will take.}
\begin{table}[h]
\caption{Analyzed vocabularies}
\begin{tabular}{|p{2.5cm}|p{6cm}|p{2cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|p{.5cm}|}
\hline
\textbf{Domain} & \textbf{Vocabulary} & \textbf{CO} & \textbf{LR} & \textbf{SR} & \textbf{AR} & \textbf{CS} & \textbf{CL}\\
\hline
Media & GTAA & & & & & & \\
\hline
Science & Geonames Ontology &&&&&& \\
\hline
& MeSH &&&&&& \\
\hline
& Peroxisome Knowledge Base &&&&&& \\
\hline
Government & Eurovoc &&&&&& \\
\hline
& IPSV &&&&&& \\
\hline
\\
\hline

\end{tabular}
\end{table}

>>>>

\subsection{Vocabulary Data Set}
Our vocabulary dataset covers XY vocabularies from various domains differing in statistical properties (cf. Table~\ref{vocabs}). The data was gathered in different ways. Some vocabularies where downloaded from their respective project websites or, in the cases of IPSV, Peroxisome Knowledge Base, and LVAk requested directly from the creators. The MeSH dataset was created by \cite{Assem2006} and is available for download\footnote{\url{http://thesauri.cs.vu.nl/eswc06/}}. We created the SKOS version of LVAk thesaurus from CSV files provided by the vocabulary maintainers. The vocabulary structure was uncomplex, so the conversion process to SKOS turned out as being rather straightforward. \todo{CM}{should we elaborate more on the conversion process?}

Our syntactical checks showed that only the Agrovoc vocabulary contained invalid datatypes and characters. After some minor syntax modifications, which don’t influence the evaluation against our criteria, we were also able to include this vocabulary. We also informed the AGROVOC team about this problem, which will try to fix it.

\begin{table}[h]
\caption{Analyzed vocabularies}
\begin{tabular}{|p{2cm}|p{6cm}|p{1.5cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|p{.8cm}|}
\hline
\textbf{Domain} & \textbf{Vocabulary} & \textbf{CO} & \textbf{LR} & \textbf{SR} & \textbf{AR} & \textbf{CS} & \textbf{CL}\\
\hline
Media & Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & & & & & & \\
\hline
Science & Geonames Ontology &&&&&& \\
\hline
& Medical Subject Headings (MeSH) &&&&&& \\
\hline
& Peroxisome Knowledge Base &&&&&& \\
\hline
Government & Eurovoc &&&&&& \\
\hline
& Integrated Public Sector Vocabulary (IPSV) &&&&&& \\
\hline
Publications & Agrovoc &&&&&& \\
\hline
& DBpedia Categories &&&&&& \\
\hline
& University of Southampton Pressinfo &&&&&& \\
\hline
& New York Times People &&&&&& \\
\hline
& Library of Congress Subject Headings (LCSH) &&&&&& \\
\hline
Cross-domain & Meketre &&&&&& \\
\hline
Economy & Thesaurus for Economics (STW) &&&&&& \\
\hline
& North American Industry Classification System (NAICS) &&&&&& \\
\hline
Military & Thesaurus Landesverteidigungsakademie (LVAk) &&&&&&
\\
\hline
\end{tabular}
\label{vocabs}
\end{table}
